# Methodology

```{r setup, include = FALSE}
# load R libraries here; the `include` flag in the chunk options above tells
# whether to print the results or not. Usually you don't want to print the
# library statements, or any code on the pdf.
# Main Packages ========
# I use these in every doc
library(tidyverse)
library(knitr)
library(kableExtra)
library(modelsummary)
options(dplyr.summarise.inform = FALSE)
# Other packages ------
# These sometimes get used, and sometimes don't.
library(mlogit)
# Instructions and options =========
# prints missing data in tables as blank space
options(knitr.kable.NA = '') 
# tells kableExtra to not load latex table packages in the chunk output
options(kableExtra.latex.load_packages = FALSE) 
# round and format numbers that get printed in the text of the article.
inline_hook <- function(x) {
  if (is.numeric(x)) {
    format(x, digits = 3, big.mark = ",")
  } else x
}
knitr::knit_hooks$set(inline = inline_hook)
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
# options for latex-only output
if(knitr::is_latex_output()) {
  knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
} 
```

In this chapter, you describe the approach you have taken on the problem. This usually involves a discussion about both the data you used and the models you applied.

## Data

Discuss where you got your data, how you cleaned it, and any assumptions you made. In this example, we get the `Car` dataset from the `mlogit` [@mlogit] package[^03_methods-1] and massage it to be in the format needed for `mlogit`.

[^03_methods-1]: You can often get a well-formatted citation for an R package by typing `citation(package = "packagename")` in the console.

```{r load_data}
data("Car", package = "mlogit")
car_mlogit <- Car %>%
  mutate(choice = gsub("choice", "", choice)) %>%
  dfidx( varying = 5:70, shape = "wide", choice = "choice", sep = "")
```

Often there will be a table describing summary statistics of your dataset. @tbl-summary shows a nice table using the [`datasummary`](https://vincentarelbundock.github.io/modelsummary/articles/datasummary.html) functions in the `modelsummary` package [@modelsummary].

```{r datasummary}
#| label: tbl-summary
#| tbl-cap: Descriptive Statistics of Dataset
datasummary_balance(
  ~type, 
  data = car_mlogit %>% 
    select(type, fuel, price, range, size), 
  dinm = FALSE
) %>%
  kableExtra::kable_styling(latex_options="scale_down")
```

## Models

If your work is mostly a new model, you probably will have introduced some details in the literature review. But this is where you describe the mathematical construction of your model, the variables it uses, and other things. Some methods are so common (linear regression) that it is unnecessary to explore them in detail. But others will need to be described, often with mathematics. For example, the probability of an alternative $i$ in the a multinomial logit model is

$$
P_i(X_{in}) = \frac{e^{X_{in}\beta_i}}{\sum_{j \in J}e^{X_{jn}\beta_j}}
$$ {#eq-mnl}

Use [LaTeX mathematics](https://www.overleaf.com/learn/latex/mathematical_expressions). You'll want to number display equations so that you can refer to them later in the manuscript. Other simpler math can be described inline, like saying that $i, j \in J$. Details on using equations in Quarto are available [here](https://quarto.org/docs/visual-editor/technical.html#equations).

You can also refer back to numbered equations, like the probability of an MNL 
presented in @eq-mnl.
