# Methodology

```{r setup, file = "R/chapter_start.R", include = FALSE}
# a number of commands need to run at the beginning of each chapter. This
# includes loading libraries that I always use, as well as options for 
# displaying numbers and text.
```

In this section, you describe your approach to the problem that you are addressing. Often, this section will contain more citations to the literature, particularly if you are using a model that someone else has developed, or a dataset that someone else has collected. In general, you should describe the process in sufficient detail that someone else could replicate your work if they had access to the same data and code.

This is the section with the most mathematics. Use numbered equation environments, and define all terms. For example, the standard linear model is described as 

$$ 
y = X\beta + \epsilon 
$$ {#eq-reg}

where $y$ is the dependent variable, $X$ is a matrix of independent variables, $\beta$ is the vector of coefficients, $\epsilon$ is the error term. Equations are part of the text, and do not "float" like figures
or tables. As such, you do not need to "introduce" equations with their number. But if you refer to them again, you should reference them, like the regression model described in @eq-reg.

You should share your data and code as feasible. Include a reference to your project's GitHub repository.
If the data are public and you can fit them in the repository, put them there.

Figures and tables should be numbered and referenced in the text. Table captions are titles, and not sentences like figures. Captions are placed above the table, but Quarto or LaTeX will handle this for you. Tables generally have only horizontal lines, and only the lines that are critical to separate blocks of information. I like using the [`modelsummary`](https://modelsummary.com) package to make tables. Use publication-ready names instead of the variable names in your table.

```{r}
#| label: tbl-sum
#| tbl-cap: Data Summary by Cylinders
datasummary_balance(~ Cylinders, dinm = FALSE,
  data = mpg |> 
    select("Miles per Gallon" = hwy, "Engine Displacmeent (liters)" = displ, "Cylinders" = cyl, "Class" = class) 
)
```