# Results
In this section, you present the results of the methods that you outlined in the previous section.
This may include estimated models, summary analyses, and visualizations with accompanying descriptive analysis.

 For example @fig-reg shows the 
data from a regression model like the one described in @eq-reg. Axes should be clearly labeled with any relevant units. I prefer the `theme_bw` function from the `ggplot2` package to make my figures look nice, with colors
for continuous data from the [`viridis`](https://sjmgarnier.github.io/viridis/) package and colors for categorical data from the [`wesanderson`](https://github.com/karthik/wesanderson) package. Figure captions are sentences that describe the figure. They generally come below the figure, but Quarto or LaTeX will handle this for you.

```{r}
#| label: fig-reg
#| fig-cap: Relationship between engine displacement and vehicle fuel efficiency.
ggplot(data = mpg, aes(x = displ, y = hwy, color = class)) + 
  geom_point() + theme_bw() + 
  stat_smooth(method = "lm", color = "black", size = 0.5) +
  scale_color_manual("Class", values = wes_palette("Zissou1", 7, type = "continuous")) +
  xlab("Engine Displacement (liters)") + ylab("Highway Miles per Gallon (mpg)")
```

@tbl-reg shows the estimated regression coefficients for the model described in @eq-reg.

```{r}
#| label: tbl-reg
#| tbl-cap: Regression Estimates
lm <- lm(hwy ~ displ + class, data = mpg)
coefmap <- c(
    "(Intercept)" = "Intercept",
    "displ" = "Engine Displacement [liters]",
    "classcompact" = "Class: Compact",
    "classmidsize" = "Class: Midsize",
    "classminivan" = "Class: Minivan",
    "classsubcompact" = "Class: Subcompact",
    "classsuv" = "Class: SUV",
    "classpickup" = "Class: Pickup"
)
modelsummary(lm, coef_rename = coefmap)
```


## Targets

If you use the [`targets`](https://docs.ropensci.org/targets/) package, you can use the `tar_make()` function to run your analysis and save the results. This is a great way to make sure that your analysis is reproducible. You can also use `tar_read()` to read in the results of your targets, and then build them into your report.

```{r, echo = TRUE, eval = FALSE}
tar_load(analysis_data)
head(analysis_data)
```


## Additional Analysis

Usually, it is good to use your model for something.

-   Hypothetical policy analysis
-   Statistical validation effort
-   Equity or impact analysis

If the additional analysis is substantial, it might become its own top-level section.
